Atomify - a live LAMMPS visualizer

### 2017-06-16 ms.tex
Update figure dummy texts

\begin{abstract}
%
The typical workflow when developing LAMMPS scripts includes working with
several programs.
A text editor is needed to modify the scripts,
the terminal to run the simulation, and programs like VMD or Ovito to visualize
the system over time.
If physical quantities are computed, the data is often plotted with MATLAB or
Python, where additional scripts must be used.
This is a tedious process, especially for teaching purposes and for people who
are new to LAMMPS.
We here introduce Atomify;
a high performance live visualizer for LAMMPS simulations,
with stunning graphics able to simulate and render more than 250000 atoms with
excellent frame rate on modern hardware.
Atomify supports OpenMP acceleration, live plotting of LAMMPS variables and
computes, and an easy-to-use code editor in one single program.
Direct access to the powerful machinery already built into LAMMPS allows easy
access to advanced physical quantities.
Atomify is open-source software (GPL) written in C++ using the Qt framework.
%
\end{abstract}

@@

A simplified version of Atomify is made available for mobile platforms (Android
and iOS).
This version of Atomify provides access to some of the examples and is intended
for exploration of molecular dynamics simulations by students.
It also works as a demonstration of the visualization capabilities of the
desktop version of the software.
The authors are optimistic that teachers can use the visualizations provided by
Atomify to explain microscopic interactions underlying concepts in topics such
as thermodynamics, geophysics, and biology.
\begin{figure*}
	\centering
	\includegraphics[width=0.95\textwidth]{gui.png}
	\caption{Overview of the Graphical User Interface (GUI) in Atomify.}
	\label{fig:gui}
\end{figure*}
\section{Features}

@@

In LAMMPS, computes are values calculated based on properties of the running
simulation.
Variables are user defined expressions which can be used to combine values in
calculations.
Once defined in a LAMMPS script, these can be plotted as a function of time in
Atomify.
This is done by clicking the name of the variable or compute in the simulation
tab.
We will explore plots in further detail in the following section.

TODO: fixes \\

@@

\begin{figure}
	\centering
	\includegraphics[width=0.3\textwidth]{dashboard.png}
	\caption{Dashboard}
	\label{fig:gui}
\end{figure}

@@

\begin{figure}
	\centering
	\includegraphics[width=0.5\textwidth]{final_billboard.png}
	\caption{Data pipeline (lammps -> atomify)}
	\label{fig:gui}
\end{figure}

@@

\subsection{Live plotting}

Live plotting is implemented using Qt Charts and Qt Data Visualization,
which are part of the Qt framework.
The data is extracted using LAMMPS' C++ API and converted to Qt datatypes before
visualization.

\subsection{Data pipeline}

When rendering one often wants to modify the data
from LAMMPS before it is visualized.
Examples are periodic images of the simulation,
slicing and coloring.
We have been inspired by the pipeline used in Ovito where the data flows through
several \textit{modifiers}, each modifying the visualization data before the
data is converted to a format for the GPU.

\section{Rendering techniques}

@@

@@

% \bibliographystyle{plain}
\bibliography{Remote}

>>>>

\begin{abstract}
%
The typical LAMMPS workflow includes working with a text editor to modify
scripts, the terminal to run simulations, and programs like VMD or Ovito to
visualize trajectories.
If physical quantities are computed, the data is often plotted with MATLAB or
Python, where additional scripts must be used.
This is a tedious process, especially for teaching purposes and for people who
are new to LAMMPS.
We here introduce Atomify;
a high performance live visualizer for LAMMPS simulations,
with stunning graphics able to simulate and render more than 250,000 atoms with
excellent frame rate on modern hardware.
Atomify supports OpenMP and GPU acceleration, live plotting of LAMMPS variables
and computes, and an easy-to-use code editor in one single program.
Direct access to the powerful machinery already built into LAMMPS allows easy
access to advanced physical quantities.
Atomify is open-source software (GPL) written in C++ using the Qt framework.
%
\end{abstract}

@@

A simplified version of Atomify is made available for mobile platforms (Android
and iOS).
This version of Atomify provides access to some of the examples and is intended
for exploration of molecular dynamics simulations by students.
It also works as a demonstration of the visualization capabilities of the
desktop version of the software.
The authors are optimistic that teachers can use the visualizations provided by
Atomify to explain microscopic interactions underlying concepts in topics such
as thermodynamics, geophysics, and biology.
\begin{figure*}
	\centering
	\includegraphics[width=0.95\textwidth]{gui.png}
	\caption{%
    Overview of the Graphical User Interface (GUI) in Atomify.
    The toolbar (1) provides changing
    between editing, viewing and analyzing the running simulation,
    in addition to playback controls.
    The file browser (2) contain the list of open LAMMPS scripts or data files.
    The text editor (3) provides code highlighting.
    The viewport (4) shows the current simulation.
    The simulation properties (5) shows the simulations details, gives access to 
    LAMMPS objects such as groups, regions and computes, and the rendering
    properties (6) lets you change the viewport settings, such as lighting and
    draw mode.
    TODO: Add numbers to figure.
    }
	\label{fig:gui}
\end{figure*}
\section{Features}

@@

In LAMMPS, computes are computations performed on a group of atoms.
Variables are user defined expressions which can be used to combine values in
calculations.
Once defined in a LAMMPS script, these can be plotted as a function of time in
Atomify.
This is done by clicking the name of the variable or compute in the simulation
tab.
We will explore plots in further detail in the following section.

Any operations that is applied to the system in a LAMMPS timestep or
minimization step is called a ``fix''.
These fixes are defined in the LAMMPS script using the ``fix'' keyword.
Atomify registers all defined fixes and lists these in the dashboard.

@@

\begin{figure}
	\centering
	\includegraphics[width=0.3\textwidth]{dashboard.png}
	\caption{Dashboard}
	\label{fig:dashboard}
\end{figure}

@@

@@

\begin{figure}
	\centering
	\includegraphics[width=0.5\textwidth]{figures/data-pipeline.pdf}
	\caption{Rendering in Atomify is based on modifying the data from LAMMPS
    by coloring, producing periodic images, and generating bonds between atoms.
    The data is extracted from LAMMPS using the library API and by accessing
    the core classes.}
	\label{fig:data-pipeline}
\end{figure}

The data pipeline from LAMMPS to rendering in Atomify is illustrated in figure
\ref{fig:data-pipeline}.
When rendering one often wants to modify the data from LAMMPS before it is
visualized.
Examples are periodic images of the simulation,
slicing and coloring.
We have been inspired by the pipeline used in Ovito where the data flows through
several \textit{modifiers}, each modifying the visualization data before the
data is converted to a format for the GPU.

\subsection{Rendering techniques}

@@

The simple case study showed how Atomify can be used for quick iteration in

@@

\section{Disclosure}

Svenn-Arne Dragly is employed part-time by The Qt Company.

\bibliography{Remote}
